---
title: My YouTube Engagement Analysis
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTFPhlseVC8C_DG8O5FgIeq88eSG7cXLjYchqI7YV-ffjgfFILLzxtDMA1L7Wz79MURXMizGgdwjVM4/pub?gid=1282172722&single=true&output=csv")
 
# Rename the variables
latest_data <- logged_data %>%
  rename(
    video_type = `What YouTube video did you watch?`,
    watch_time = `When did you watch this video?`,
    video_length = `How long was the video? (minutes, only need to tell us the number`
  )

# Convert video_length to numeric
latest_data <- latest_data %>%
  mutate(video_length = as.numeric(video_length))

# 1. Summary Values

# a. Average video length
mean_video_length <- latest_data %>%
  summarize(mean_length = mean(video_length, na.rm = TRUE))

# b. Minimum video length
min_video_length <- latest_data %>%
  summarize(min_length = min(video_length, na.rm = TRUE))

# c. Maximum video length
max_video_length <- latest_data %>%
  summarize(max_length = max(video_length, na.rm = TRUE))

# d. Number of responses for each video type
video_type_counts <- latest_data %>%
  group_by(video_type) %>%
  summarize(count = n())

# e. Number of responses for each watch_time
watch_time_counts <- latest_data %>%
  group_by(watch_time) %>%
  summarize(count = n())

# f. Total number of responses
total_responses <- nrow(latest_data)

# 2. Bar Charts

# a. Bar chart of video types
video_type_plot <- ggplot(latest_data, aes(x = video_type)) +
  geom_bar(fill = "#FFFF00") +
  labs(
    title = "Distribution of Watched Video Types",
    x = "Video Type",
    y = "Number of Responses"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# b. Bar chart of watch times
watch_time_plot <- ggplot(latest_data, aes(x = watch_time)) +
  geom_bar(fill = "#440154FF") +
  labs(
    title = "Distribution of Watch Times",
    x = "Time of Day",
    y = "Number of Responses"
  ) +
  theme_minimal()


```

```{css}
/* Add some basic styling */
body {
  font-family: sans-serif;
  line-height: 1.6;
  color: #333;
  background-color: #f0f0f0; /* Light gray background */
  padding: 20px;
}

h1, h2, h3 {
  color: #0056b3;
}

h2 {
  border-bottom: 2px solid #0056b3;
  padding-bottom: 5px;
  margin-top: 30px;
}

p {
  margin-bottom: 15px;
}

.plot-container {
  margin-top: 20px;
  border: 1px solid #ddd;
  padding: 10px;
  background-color: #fff;
  border-radius: 5px;
}

/* Style the dynamic comments */
.dynamic-comment {
  font-style: italic;
  color: #777;
}

/* Style for plot titles */
.plot-title {
  font-size: 1.2em;
  font-weight: bold;
  margin-bottom: 10px;
}
```


## My YouTube Engagement Analysis

This report analyzes data on my YouTube viewing habits, focusing on video types, watch times, and video lengths.

**Summary Statistics**

*   Average video length watched was `r round(mean_video_length$mean_length, 2)` minutes.
*   The shortest video watched was `r min_video_length$min_length` minutes, and the longest was `r max_video_length$max_length` minutes.

## Video Type Distribution


```{r video-type-plot-chunk, fig.width=6, fig.height=4}  
print(video_type_plot)

```



## Watch Time Analysis

```{r watch_time_plot, fig.width=6, fig.height=4}  
print(watch_time_plot)

```


